---
title: "CH_14_Demo_Code"
author: "Dr. Luedeker"
date: "4/2/2014"
output: pdf_document
---

Chapter 14 is about making professional looking plots and arranging multiple plots on the same figure.  This is an important skill to have when writing a paper in the sciences.

```{r message=FALSE, warning=FALSE}
library(tidyverse)   # loading ggplot2 and dplyr
library(patchwork)   # arranging multiple graphs into 1 figure
library(viridis)     # The viridis color schemes
library(latex2exp)   # For plotting math notation
```

## Part one: Multiple Plots

First we will create and store some plots to work with.

```{r}
P1 <- ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + 
  geom_point(size=3)  + labs(title='P1 - Iris')
P2 <- ggplot(trees, aes(x=Height, y=Volume, color=Girth)) + 
  geom_point()  + labs(title='P2 - Cherry Trees')
P3 <- ggplot(iris, aes(x=Sepal.Length)) + 
  geom_histogram(bins=30) + labs(title='P3 - Iris')
P4 <- ggplot(iris, aes(x=Species, y=Sepal.Length, fill=Species)) + 
  geom_boxplot() + labs(title='P4 - Iris')
```

Using the package cowplot and the funtction plot grid.

```{r fig.height=6, fig.width=10}
cowplot::plot_grid(P1, P2, P3, P4, nrow=2, ncol=3, labels=c('A','B','C'))
```

With a different number of rows and columns.  Need to adjust figure height and figure width in the code chunk options.

```{r}

```

Using the package patchwork.  All you have to do is "add" plots.

All the same size
```{r}
 P1 + P2 + P3 + P4
```

With groupings.  Parentheses create grouping, slash creates rows, vertical lines create columns.

```{r}
(P1 | P2) / P3 
```

```{r}
(P1 + P2) | P3 
```

```{r}
(P1 | (P2/P4)) + 
  plot_annotation(
    title = 'Composite Graph Title',
    subtitle = 'With a compelling subtitle',
    caption = 'Iris Data from Edgar Anderson (1935)'
  ) 
```

```{r}
(P1 | (P2/P4)) + 
  plot_annotation(title = 'Composite Graph Title') +
  plot_layout(guides = 'collect')
```

```{r}
((P1 + theme(legend.position = 'none')) | (P2/P4)) +
  plot_annotation(
    title = 'Composite Graph Title',
    subtitle = 'With a compelling subtitle',
    caption = 'Iris Data from Edgar Anderson (1935)') +
  plot_layout(guides = 'collect')
```

## Part 2: Color Palettes

You can change colors many different ways, one is to use brewer color palettes.

```{r}
cowplot::plot_grid(
  P1 + scale_color_brewer(palette='Dark2'),
  P4 + scale_fill_brewer(palette='Dark2') 
  )
```

Or use viridis

```{r}
cowplot::plot_grid(
  P1 + scale_color_viridis_d(option='plasma'),      # _d for discrete
  P2 + scale_color_viridis_c( option='viridis') )   # _c for continuous
```

## Part 3: Themes

Themes are "added" to a plot to change the look of the plot.

```{r}
Rmisc::multiplot( cols = 2,
  P1 + theme_bw()      + labs(title='theme_bw'), # Black and white
  P1 + theme_minimal() + labs(title='theme_minimal'),   
  P1 + theme_dark()    + labs(title='theme_dark'),        
  P1 + theme_light()   + labs(title='theme_light')
)
```


## Part 3: Mathematical notation 

Use Latex to Expression to type in math mode on a plot.


Simulate some data
```{r}
seed <- 7867
N <- 20
data <- data.frame(x=runif(N, 1, 10)) %>%    # create a data set to work with
  mutate(y = 12 - 1*x + rnorm(N, sd=1))      # with columns x, y

model <- lm( y ~ x, data=data)               # Fit a regression model
data <- data %>%                             # save the regression line yhat points
  mutate(fit=fitted(model))
```

Create the plot with mathematical notation.
```{r}
ggplot(data, aes(x=x)) +
  geom_point(aes(y=y)) +
  geom_line(aes(y=fit), color='blue') +
  annotate('text', x=9, y=9.5, 
           label=latex2exp::TeX('$\\hat{\\rho}$ = 0.916') ) +   # always double \\
  labs( x=latex2exp::TeX('X-axis $\\alpha$'), 
        y=latex2exp::TeX('Y: $\\log_{10}$(Income)'),
        title=latex2exp::TeX('Linear Models use: $\\hat{\\beta} = (X^TX)^{-1}X^Ty$'))
```



