---
title: "CH_11_Demo_Code"
author: "Dr. Luedeker"
date: "`r Sys.Date()`"
output: pdf_document
---

Chapter 11 requires us to use the package stringr.  However, stringr is a package contained in the tidyverse suite.  Hence, we can just load tidyverse.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

## Part One: Paste

Paste glues character strings with stored objects, numbers, other character strings, and mathematical expressions.  It is a base R function.

```{r}

```

## Part Two: separate

separate is a function that works on a dataframe.  You give it a column that contains character strings that need to be broken into multiple columns based on some pattern.  Use can use and and or with these.

```{r}
exdata <- data.frame(mystrings = c("Hi.there.2.3.5", "78.90.65.Bye.Loser") )
separate(exdata, mystrings, into = c("A", "B", "C", "D", "Excellent"), sep="\\.")

```

## Part Three: My favorite str functions

Demo str_split and str_length.

```{r}
phrase <- "A.man.a.plan.a.canal.Panama"
str_split(phrase, "\\.")[[1]] %>%
  str_length()
```

Demo the difference between str_replace and str_replace_all.
```{r}
str_replace(phrase, pattern="\\.", replacement=" ")
str_replace_all(phrase, pattern="\\.", replacement=" ")
```

Demo str_sub.

```{r}
phrases <- c("A.man.a.plan.a.canal.Panama", "I.eat.tomato.soup.everyday")
str_sub(phrases, start=7, end=12)
```


