---
title: "Bianca's Notes for CH 8"
author: "Bianca Luedeker"
date: "2024-02-27"
output: pdf_document
---

Load pacakges

## Vectors

a. Using seq count by 4
```{r}
seq(from=1, to=4, by=1)
```

b. Make a vector of length 100 where the numbers are evenely sapced.
```{r}
abc<- seq(from=105, to=905, length.out=100)
```

c. The negative notation.
```{r}
abc <- aa[c(-8, -31:-100)]
abc
```



## Matrices

a. Construct a matirx with 6 rows and 4 columns.
```{r}
e <- matrix(abc, nrow=6, ncol=4, byrow=TRUE)
e
```

b. cbind 
```{r}
c1 <- c(15, 7, 23)
c2 <- c(1, 2.5, 4)
c3 <- c(13, 16, 7)
cbind(c1, c2, c3)
```

c. rbind
```{r}
rbind(c1, c2, c3)
```

d. Extact an element
```{r}
e[1,3]
```

e. Extract a row
```{r}
e[1,]
```

f. Extract a column.
```{r}
e[,2]
```

## Data Frames

a. Construct a dataframe.
```{r}
my.df <- data.frame( height = c(2, 3),
                     weight = c(4, 5))
```

b. Extract a column.
```{r}
my.df$height
me.df[, 1]
```

c. Extract a value.
```{r}
my.df[2, 1]
```
## Lists
a. Construct a list of unlike objects.
```{r}
my.list <- list(vec = aa, matrix = e, df = my.df)
my.list
```

b. Extract using dollar sign notation.
```{r}
my.list$df
```

c. Extract using single brackets.
```{r}
my.list[1]
str(my.list[1])
```

d. Extract using double brackets.  What is the difference?
```{r}
my.list[[1]]
str(my.list[[1]])
```
The difference is that now the list is made up as numbers instead of as a vector

e. lm is a list.  Show what is in lm.
```{r}
data('iris')
mod <- lm(data=iris, Petal.Length~Petal.Width)

lm(mod)
```

