---
title: "STA 445 HW2"
author: "Nicholas Larson"
date: "2/27/24"
output: pdf_document
---

## Problem 1

Create a vector of three elements (2,4,6) and name that vector `vec_a`. Create a second vector, `vec_b`, that contains (8,10,12). Add these two vectors together and name the result `vec_c`.
```{r}
vec_a <- c(2,4,6)
vec_b <- c(8,10,12)
vec_c <- vec_a+vec_b
vec_c
```


## Problem 2

Create a vector, named `vec_d`, that contains only two elements (14,20). Add this vector to `vec_a`. What is the result and what do you think R did (look up the recycling rule using Google)? What is the warning message that R gives you?
```{r}
vec_d <- c(14,20)
vec_a+vec_d
```
R warned me that vec_a is three objects long while vec_d is only 2 objects long.

## Problem 3

Next add 5 to the vector vec_a. What is the result and what did R do? Why doesn't in give you a warning message similar to what you saw in the previous problem?
```{r}
vec_a+5
```
It didnt give a warning presumably because R knew I wanted to add 5 to all numbers, but because there were two numbers in the previous problem, R didnt know what to do. R couldnt add two lists/vector that are incompatible with each other.


## Problem 4

Generate the vector of integers $\left\{ 1,2,\dots5\right\}$ in two different ways. 

a.  First using the `seq()` function
```{r}
seq(from=1, to=5, by=1)
```

b. Using the `a:b` shortcut.
```{r}
1:5
```


## Problem 5

Generate the vector of even numbers $\left\{ 2,4,6,\dots,20\right\}$ 

a. Using the seq() function  
```{r}
seq(from=2, to=20, by=2)
```

b. Using the a:b shortcut and some subsequent algebra. 
```{r}
y <- 1:10*2
y
```


## Problem 6

Generate a vector of 21 elements that are evenly placed between 0 and 1 using the `seq()` command and name this vector `x`. 
```{r}
x <- seq(from=0, to=1, length.out=21)
x
```


## Problem 7

Generate the vector $\left\{ 2,4,8,2,4,8,2,4,8\right\}$ using the `rep()` command to replicate the vector c(2,4,8). 
```{r}
rep( c(2,4,8), 3)
```
  

## Problem 8
Generate the vector $\left\{ 2,2,2,2,4,4,4,4,8,8,8,8\right\}$
using the `rep()` command. You might need to check the help file for rep() to see all of the options that rep() will accept. In particular, look at the optional argument `each=`.
```{r}
rep( c(2,4,8), each=4)
```

  
## Problem 9 

In this problem, we will work with the matrix 
$$ \left[\begin{array}{ccccc}
    2 & 4 & 6 & 8 & 10\\
    12 & 14 & 16 & 18 & 20\\
    22 & 24 & 26 & 28 & 30
    \end{array}\right]$$
    
a.  Create the matrix in two ways and save the resulting matrix as `M`.

i. Create the matrix using some combination of the `seq()` and `matrix()` commands.
```{r}
m <- seq(1:15)*2
matrix(m, ncol=5, nrow=3, byrow=TRUE)
```

ii. Create the same matrix by some combination of multiple `seq()` commands and either the `rbind()` or `cbind()` command.
```{r}
r1 <- seq(1:5)*2
r2 <- seq(from=12, to=20, by=2)
r3 <- seq(22, 30, length.out=5)
nmat <- rbind(r1,r2,r3)
nmat
```

b. Extract the second row out of M.
```{r}
nmat[2,]
```

c. Extract the element in the third row and second column of M
```{r}
nmat[3,2]
```


## Problem 10 

The following code creates a `data.frame` and then has two different methods for removing the rows with `NA` values in the column `Grade`. Explain the difference between the two.

```{r, eval=FALSE}
df <- data.frame(name= c('Alice','Bob','Charlie','Daniel'),
                     Grade = c(6,8,NA,9))
    
df[ -which(  is.na(df$Grade) ), ]

df[  which( !is.na(df$Grade) ), ]
```
In the first strategy, the negation is in the 'which()' function, the code selects the N/A value, then uses everything else. While in the second strategy, the negation is in the 'is.na' function, the code selects all values not N/A, and uses those values selected.


## Problem 11 

Create and manipulate a list.

a.  Create a list named my.test with elements
        + x = c(4,5,6,7,8,9,10)
        + y = c(34,35,41,40,45,47,51)
        + slope = 2.82
        + p.value = 0.000131
```{r}
x = c(4,5,6,7,8,9,10)
y = c(34,35,41,40,45,47,51)
slope = 2.82
p.value = 0.000131
my.test <- list(xcoord = x, ycoord = y, slope = slope, p_value = p.value)
my.test
```

b.  Extract the second element in the list.
```{r}
my.test[2]
```

c.  Extract the element named `p.value` from the list.
```{r}
my.test$p_value
```


