---
title: "STA_445_Assignment_6"
author: "Nicholas Larson"
date: base::Sys.Date()
output: pdf_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
```

## Problem 1
Convert the following to date or date/time objects.

a. September 13, 2010.
```{r}
mdy('September 13, 2010')
```

b. Sept 13, 2010.
```{r}
as.Date('Sept 13, 2010', format='%b %d, %Y')
```
*This one doesnt work because r does not recognize 'Sept' as a month, only its three character form or its full form.*

c. Sep 13, 2010.
```{r}
as.Date('Sep 13, 2010', format='%b %d, %Y')
```

d. S 13, 2010. Comment on the month abbreviation needs.
```{r}
mdy('S 13, 2010')
```
*In order to be read correctly, the month needs to be either fully complete or 3 characters long, not 1, not 4.*

e. 07-Dec-1941.
```{r}
dmy('07-Dec-1941')
```

f. 1-5-1998. Comment on why you might be wrong.
```{r}
mdy('1-5-1998')
```
*I cannot be sure whether the '1' or the '5' is the month or day as they both make sense.*

g. 21-5-1998. Comment on why you know you are correct.
```{r}
dmy('21-5-1998')
```
*I know this is the true answer because there is not 21 months in the year, so it must be the day.*

h. 2020-May-5 10:30 am
```{r}
ymd_hm('2020-May-5 10:30 am')
```

i. 2020-May-5 10:30 am PDT (ex Seattle)
```{r}
ymd_hm('2020-May-5 10:30 am', tz="US/Pacific")
```

j. 2020-May-5 10:30 am AST (ex Puerto Rico)
```{r}
ymd_hm('2020-May-5 10:30 am', tz="America/Virgin")
```

### Problem 2

Using just your date of birth (ex Sep 7, 1998) and today's date calculate the following:

a. Calculate the date of your 64th birthday.
```{r}
bday <- mdy('02042003')
bday + years(64)
```

b. Calculate your current age (in years). 
```{r}
bday <- mdy('02042003')
exactbday <- as.period(bday %--% base::Sys.Date())
year(exactbday)
```

c. Using your result in part (b), calculate the date of your next birthday.
```{r}
nbday <- bday + years(22)
nbday
```

d. The number of _days_ until your next birthday.
```{r}
dtil <- as.period(base::Sys.Date() %--% nbday)
as.period(dtil, unit='days')
```

e. The number of _months_ and _days_ until your next birthday.
```{r}
dtil <- as.period(base::Sys.Date() %--% nbday)
as.period(dtil, unit='months')
```


## Problem 3

Suppose you have arranged for a phone call to be at 3 pm on May 8, 2015 at Arizona time. However, the recipient will be in Auckland, NZ. What time will it be there? 
```{r}
mdy_h('May 8, 2015 3pm', tz='US/Arizona') %>% with_tz("NZ")
```


## Problem 4

It turns out there is some interesting periodicity regarding the number of births on particular days of the year.

a. Using the `mosaicData` package, load the data set `Births78` which records the number of children born on each day in the United States in 1978. Because this problem is intended to show how to calculate the information using the `date`, remove all the columns *except* `date` and `births`. 
```{r}
library(mosaicData)
data("Births78")
Births78 <- Births78 %>% select(date, births)
head(Births78)
```

b. Graph the number of `births` vs the `date` with date on the x-axis. What stands out to you? Why do you think we have this trend?
```{r}
ggplot(data=Births78, aes(x=date, y=births)) + geom_point()
```
*I am not sure why that could be, but the next problem talks about days of the week, so that probably has something to do with it.*

c. To test your assumption, we need to figure out the what day of the week each observation is. Use `dplyr::mutate` to add a new column named `dow` that is the day of the week (Monday, Tuesday, etc). This calculation will involve some function in the `lubridate` package and the `date` column.
```{r}
Births78 <- Births78 %>% mutate(
  dow = format(date, '%A')
)
head(Births78)
```

d. Plot the data with the point color being determined by the day of the week variable.
```{r}
ggplot(data=Births78, aes(x=date, y=births)) + geom_point(aes(color=dow))
```
```










